Reducing Linearizability of Priority Queues and More Data Structures to State Reachability

### 2017-04-21 co-regular-EPQ.tex
introduction
modify

Assume that $x$ is covered by $d_1,\ldots,d_m$, we can safely rename $x$ into $b$, rename $d_1,\ldots,d_m$ into $a$ and rename all other value into $c$ by data-independence. Such execution can be recognized by register automata, since between the first $\textit{ret}(\textit{put},a,\_)$ and the last $\textit{call}(\textit{rm},a)$ (if exists), $\textit{ret}(\textit{put},a,\_)$ and $\textit{call}(\textit{rm},a)$ occurs in pair and there is no need for count. In Appendix \ref{sec:appendix proof and definition in section co-regular of EPQ1Lar}, we construct a set $\textit{Auts}_{\textit{1-lar}}$ of register automata, {\color {blue}and prove that $\textit{Auts}_{\textit{1-lar}}$ is $\mathsf{MatchedMaxPriority}^{>}$-complete, as stated by the following lemma.

\begin{restatable}{lemma}{EPQOneLarisCoRegular}
\label{lemma:EPQ1Lar is co-regular}
$\textit{Auts}_{\textit{1-lar}}$ is $\mathsf{MatchedMaxPriority}^{>}$-complete.
\end{restatable}
}

{\color {blue}
For example, to capture non-$\mathsf{MatchedMaxPriority}^{>}$-linearizable execution $e$ where $e \vert_{b} = \textit{call}(\textit{put},b,\_) \cdot \textit{ret}(\textit{put},b,\_) \cdot \textit{call}(\textit{rm},b) \cdot \textit{ret}(\textit{rm},b)$, we use the register automaton in \figurename~\ref{fig:automata APQ1Lar-1 in paper}. Here $c_1 = c + \textit{ret}(\textit{rm},a)$, $c_2 = c + \textit{call}(\textit{put},a,=r)$, $c_3 = c_2 + \textit{ret}(\textit{rm},a)$, where $c = \textit{call}(\textit{put},d,\top),\textit{ret}(\textit{put},d,\top), \textit{call}(\textit{rm},d)$, $\textit{ret}(\textit{rm},d),\textit{call}(\textit{rm},\textit{empty}),\textit{ret}(\textit{rm},\textit{empty})$. There are three paths in $\mathcal{A}_{\textit{l-lar}}^1$, since there are three possible position of  the first $\textit{ret}(\textit{put},a)$ in $e$.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1 \textwidth]{figures/PIC_AUTO_PQ1Lar-pprr.pdf}
%\vspace{-10pt}
  \caption{Automaton $\mathcal{A}_{\textit{l-lar}}^1$}
  \label{fig:automata APQ1Lar-1 in paper}
\end{figure}
}
TODO GIVE THE AUTOMATON

@@

\subsection{A $\mathsf{MatchedMaxPriority}^=$-complete automaton}
\label{subsec:co-regular of EPQ1Equal}

>>>>

{\color {blue} Assume that $x$ is covered by $d_1,\ldots,d_m$, we can safely rename $x$ into $b$, rename $d_1,\ldots,d_m$ into $a$ and rename all other value into $c$ by data-independence. Since there are four cases of projection of execution to $x$ when their is a cycle through $x$. To ease the reading, for each of such case we generate a register automata, and then let the $\mathsf{MatchedMaxPriority}^{>}$-complete automaton be the union of the four register automata. For example, for the case when the projection of $e$ to $x$ is as in \figurename~\ref{fig:introduce gap for EPQ1Lar} (rename $b$ into $x$), we construct a register automaton $\mathcal{A}_{\textit{l-lar}}^1$ in \figurename~\ref{fig:automata APQ1Lar-1 in paper}. Here transition labels $c_1 = c + \textit{ret}(\textit{rm},a)$, $c_2 = c + \textit{call}(\textit{put},a,=r)$, $c_3 = c_2 + \textit{ret}(\textit{rm},a)$, where $c = \textit{call}(\textit{put},d,\top),\textit{ret}(\textit{put},d,\top), \textit{call}(\textit{rm},d)$, $\textit{ret}(\textit{rm},d),\textit{call}(\textit{rm},\textit{empty}),\textit{ret}(\textit{rm},\textit{empty})$. There are three paths in \figurename~\ref{fig:introduce gap for EPQ1Lar} from $q_{\textit{init}}$ to $q_7$, and they comes from that there are three possible positions for the first $\textit{call}(\textit{put},a,\_)$ in the captured execution, which is shown in \figurename~\ref{fig:executions APQ1Lar-1 in paper}. In \figurename~\ref{fig:automata APQ1Lar-1 in paper}, the paths $q_1 \rightarrow q_2 \rightarrow q_3 \ldots \rightarrow q_7$, $q_1 \rightarrow q_2 \rightarrow q_3 \ldots \rightarrow q_{10}$ and $q_1 \rightarrow q_9 \rightarrow q_{10} \ldots \rightarrow q_7$ corresponds to the first, second and third cases in \figurename~\ref{fig:executions APQ1Lar-1 in paper}, respectively.
}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1 \textwidth]{figures/PIC_AUTO_PQ1Lar-pprr.pdf}
%\vspace{-10pt}
  \caption{Automaton $\mathcal{A}_{\textit{l-lar}}^1$}
  \label{fig:automata APQ1Lar-1 in paper}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1 \textwidth]{figures/PIC_HIS_PQ1Lar-pprr-in-paper.pdf}
%\vspace{-10pt}
  \caption{Three possible positions of the first $\textit{call}(\textit{put},a,\_)$ in captured execution}
  \label{fig:executions APQ1Lar-1 in paper}
\end{figure}

{\color {blue}
Let $\mathcal{A}_{\textit{1-lar}}$ be the union of the four register automata mentioned above, then we prove that $\mathcal{A}_{\textit{1-lar}}$ is $\mathsf{MatchedMaxPriority}^{>}$-complete. The detailed construction and proof can be found in Appendix \ref{sec:appendix proof and definition in section co-regular of EPQ1Lar}.
}

\begin{restatable}{lemma}{EPQOneLarisCoRegular}
\label{lemma:EPQ1Lar is co-regular}
$\textit{Auts}_{\textit{1-lar}}$ is $\mathsf{MatchedMaxPriority}^{>}$-complete.
\end{restatable}

@@

\subsubsection{A $\mathsf{MatchedMaxPriority}^=$-complete automaton}
\label{subsec:co-regular of EPQ1Equal}
